Study 1

### 2022-02-17 code/analysis.Rmd
investigate & tweak timer, add PD/BoS mix

>>>>

# Poking at time recording

Conclusion -- doing things player side is just a bad idea! and the times are worse than thought. 
```{r total-time}
# game KxJzRQeo5HikZxreo, player BkAWA2P83AnBmRcif has consistently unreasonable times (3300+, should be <180, so something's messing up)

summary %>% group_by(game_cond, chat_cond) %>% tally()
```

Empirica recommends using stages.csv startTimeAt and players-stages.csv submittedAt

```{r}
d.stages <- read_csv(here(data_location,"stages.csv")) %>% rename(stageId=`_id`)

d.player_stages <- read_csv(here(data_location,"player-stages.csv")) %>%
  left_join(d.stages) %>% 
  filter(!is.na(submittedAt)) %>% 
  mutate(timedif=submittedAt-startTimeAt)

d.player_stages %>% filter(playerId=="BkAWA2P83AnBmRcif") %>% View()

blah <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  rename(roundId=`_id`) %>% 
  select(roundId, playerId, time)
foobar <- d.player_stages %>% select(playerId, roundId, timedif) %>% left_join(blah) %>% mutate(time=as.numeric(time)/1000) %>% mutate(check=timedif-time)

View(foobar)
